Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications

### 2012-07-23 doc/asplos13/evaluation.tex
Tiny changes.

To evaluate Grappa's preformance with respect to the XMT, we ran each
of our three benchmarks on up to 16 nodes of each machine. Grappa used
6 cores per node, with the best parameters chosen for each point. The
XMT could not run on 2 nodes, so the point is omitted.

@@

We ran BFS on a synthetic Kronecker graph with $2^{25}$ vertices and
$2^{29}$ edges (25 GB of data). Figure~\ref{fig:bfs-performance} shows
our performance in terms of graph edges traversed per second . The XMT
is 2.5 times faster than Grappa at 16 nodes.

>>>>

To evaluate Grappa's performance with respect to the XMT, we ran each
of our three benchmarks on up to 16 nodes of each machine. Grappa used
6 cores per node, with the best parameters chosen for each point. In
some cases, the XMT could not run the benchmark with 2 nodes, so the
point is omitted.

@@

We ran BFS on a synthetic Kronecker graph with $2^{25}$ vertices and
$2^{29}$ edges (25 GB of data). Figure~\ref{fig:bfs-performance} shows
our performance in terms of graph edges traversed per second. The XMT
is 2.5 times faster than Grappa at 16 nodes.
